---
title: "Homework 3"
author: "Mingee Choi"
date: 10/15/2022
output: github_document
---

Load Packages

```{r setup, message=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(dplyr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 2

####Load, tidy, and wrangle accel_data.csv
```{r}
accel_df =
  read_csv("./data/accel_data.csv")%>%
  janitor::clean_names()%>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute_of_day",
    values_to = "activity_count"
  )%>%
  mutate(weekend_weekday = ifelse(day %in% c("Friday", "Saturday", "Sunday"), "weekend", "weekday"))%>%
  mutate(day=as.factor(day))%>%
  mutate(weekend_weekday=as.factor(weekend_weekday))%>%
  select(week, day_id, day, weekend_weekday, everything())
```

This dataset contains `50,400` observations of `6` variables. Variables include week, day_id, day, weekend_weekday, activity_count, and  minute_of_day.

####Aggregate across minutes to create a total activity variable for each day, create a table, and look at trends
```{r}
  accel_df$day = ordered(accel_df$day, levels=c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
  accel_df %>%
  group_by(week, day) %>%
  summarize(total_activity = sum(activity_count))%>%
 pivot_wider(
   names_from = day,
   values_from = total_activity
 ) %>%
    knitr::kable(digits = 1)
```
There aren't any obvious trends, but our 63 year-old male study was slightly more active on Monday and Friday than Tuesday-Thursday and Saturday. He was least active on Saturday, especially for week 4 and 5.

####Make a single-panel plot that shows the 24-hour activity time courses for each day
```{r}
accel_df %>%
  mutate(minute_of_day = as.numeric(minute_of_day))

accel_df %>%
  ggplot(aes(x=minute_of_day, y=activity_count, color = day)) + 
  geom_line() +
  geom_smooth(alpha = 0.5)
labs(
    title = "24-hour activity time courses for each day",
    x = "minute of day",
    y = "activity count"
  ) 
```
From the graph, it seems as if our study is least active on Tuesday and Thursday and most active on Friday, Sunday, and Monday.


# Problem 3

####load dataset
```{r}
data("ny_noaa")%>%
summary(ny_noaa)
```

NY NOAA contains 2,595,176 observations of 7 variables and contains the variables id, date, prcp, snow, snwd, tmax, and tmin.'id' represents weather station ID, 'prcp' represents precipitation(tenths of mm), 'snwd' represents snow depth, 'tmax' represents maximum temperature, and 'tmin' represents minimum temperature. There are 591,786 total missing values; missing values are a serious issue in this data set, espcially for snowfall.

####Data cleaning
```{r}
ny_noaa_tidy = ny_noaa%>%
janitor::clean_names()%>%
separate(date, into=c("year", "month", "day"))%>%
  mutate(month = month.abb[as.numeric(month)])%>% 
  mutate(
    tmax = as.numeric(tmax) / 10,
    tmin = as.numeric(tmin) / 10,
    prcp = as.numeric(prcp) / 10,
  )

mode = function(){
    return(sort(-table(ny_noaa$snow))[1])
}
mode()
```

The most commonly observed value is 0 because snow usually comes down during winter and not during the other seasons.

####Two-panel plot showing average max temperature in Jan. and in July in each station across years
```{r}
ny_noaa_tidy%>%
  filter(month %in% c("Jan", "Jul"))%>%
  group_by(id, year, month)%>%
  summarize(avg_tmax = mean(tmax, rm.na = TRUE)) %>%
    ggplot(aes(x=as.numeric(year), y=avg_tmax, color=avg_tmax))+
    geom_line(alpha = 0.4) +
    geom_point(alpha = 0.5, size = 0.5) +
    scale_x_continuous(breaks = c(1980, 1990, 2000, 2010)) +
    labs(
      title = "Averge max temperature in Janurary and July",
      x = "years",
      y = "average max temperature"
    ) +
      facet_grid(~month)
```
Average max temperature in July was much higher than January. Temperatures are relatively stable except there was one large dip (potential outlier) in average max temperature in July between 1985-1990.

####Two-panel plot showing tmax vs tmin for full dataset and make a plot showing distribution of snowfall values greater than 0 and less than 100 separately by year
```{r}
plot1 = ny_noaa_tidy%>%
  ggplot(aes(x=tmin, y=tmax, rm.na = TRUE)) +
  geom_boxplot(color='red') +
  labs(
    title= "Tmax vs Tmin",
    x = "minimum temperature",
    y = "maximum temperature"
  )

plot2 = ny_noaa_tidy%>%
  filter(snow> 0 & snow < 100) %>%
  ggplot(aes(x=as.numeric(year), y=snow)) +
  geom_boxplot(color ='blue') +
  scale_x_continuous(breaks = c(1980, 1990, 2000, 2010)) +
  labs(
    title= "Distribution of snowfall by year",
    x = "year",
    y = "distribution of snowfall"
  )
plot1 + plot2
```



