---
title: "Homework 3"
author: "Mingee Choi"
date: 10/15/2022
output: github_document
---

Load Packages

```{r setup, message=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(dplyr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 2

Load, tidy, and wrangle accel_data.csv
```{r}
accel_df =
  read_csv("./data/accel_data.csv")%>%
  janitor::clean_names()%>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute_of_day",
    values_to = "activity_count"
  )%>%
  mutate(weekend_weekday = ifelse(day %in% c("Friday", "Saturday", "Sunday"), "weekend", "weekday"))%>%
  mutate(day=as.factor(day))%>%
  mutate(weekend_weekday=as.factor(weekend_weekday))%>%
  select(week, day_id, day, weekend_weekday, everything())
```

This dataset contains `50,400` observations of `6` variables. Variables include week, day_id, day, weekend_weekday, activity_count, and  minute_of_day.

Aggregate across minutes to create a total activity variable for each day, create a table, and look at trends
```{r}
  accel_df$day = ordered(accel_df$day, levels=c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"))
  accel_df %>%
  group_by(week, day) %>%
  summarize(total_activity = sum(activity_count))%>%
 pivot_wider(
   names_from = day,
   values_from = total_activity
 ) %>%
    knitr::kable(digits = 1)
```
There aren't any obvious trends, but our 63 year-old male study was slightly more active on Monday and Friday than Tuesday-Thursday and Saturday. He was least active on Saturday, especially for week 4 and 5.

Make a single-panel plot that shows the 24-hour activity time courses for each day
```{r}
accel_df %>%
  mutate(minute_of_day = as.numeric(minute_of_day))

accel_df %>%
  ggplot(aes(x=minute_of_day, y=activity_count, color = day)) + 
  geom_line()+
  geom_smooth(alpha = 0.5)
labs(
    title = "24-hour activity time courses for each day",
    x = "minute of day",
    y = "activity count"
  ) 
```
From the graph, it seems as if our study is least active on Tuesday and Thursday and most active on Friday, Sunday, and Monday.


# Problem 3






